---
title: "Data Practical Week 3"
author: "Bastien Nespolo"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Welcome in this report !
Here we load libraries to read our next folders.
```{r message=FALSE, warning=FALSE}
library(readr)
library(dslabs)
```


# Dataset number 1 !

We will start by load our first dataset. I chose orange because it's a fruit that I really appreciate and it's the tree that I prefer.

In this dataset we have information about Trees, their circumferences and their ages. Respectively according to Qualitative (nominal) , Quantitative (discrete) and Quantitative (discrete) categories.
Just to precise my opinion, even if it's tree is represented by a number I presuppose that researchers have this number attributed to a category of tree as "pine" so for me Tree is a qualitative variable

Now, with the formula str we have an overview of variables.

```{r oranges}
data(Orange)
str(Orange)
```

# Dataset number 2 !

Now we will load a second dataset from an external source. Let's do it !

In this table we can also see all types of variables and details about them.

We can see that the only integer variable is X. Then, that Ingredient, Text, Recipe index and unit are characters variables. Finally, rating and quantity are numerical variables.

Qualitative variables are : Ingredient (nominal), Text (nominal), Recipe Index (nominal), Unit (nominal)
Quantitative variables are : Rating (continuous), Quantity (discrete)

```{r cookies}
cookies<-read.csv("https://raw.githubusercontent.com/the-pudding/data/master/cookies/choc_chip_cookie_ingredients.csv")
str(cookies)
```
# Dataset number 3 !

Now we will load a third and last dataset from the library dslabs.

Here we can analyse our stars variables.
We can see that stars' names is a Qualitative (nominal) categories. Magnitude is Quantitative (continuous), temp is Quantitative (discrete) and type is Qualitative (nominal). 

```{r stars}
data(stars)
str(stars)
```

Okay, now we see that we can analyze data and have information about them.



