---
title: "Data Practicals Week 5"
author: "Bastien Nespolo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 4

Welcome in this report !
Here we load libraries to read our next folders.
```{r message=FALSE, warning=FALSE}
library(readr)
library(dslabs)
library(dplyr)
library(knitr)
```

We will load a dataset from the package dplyr. I don't specially like starwars, even if it's nice and famous, but I chose this dataset in order to learn a bit more about it. And fun fact, my brother's name come from starwars... I let you think about who he can be. 
```{r datsaet}
data(starwars)
```

With the str formula we can have a look on types of data and describe them a bit.
```{r describe data}
str(starwars)
```

We can see that we have 11 variables which are "character" ; 2 are "numeric" and only 1 (height) is "integer".
On this dataset we can see all characters of Starwars and details about them like their mass or eye color. It could be interesting for real fans if they don't already know these information as their height. I think the most important is the film in which they are because if you are really fan of one character you can directly know where you can follow his/her adventures.

Now we will make our data long in place of wide. For that we will need to use the package "tidyverse" that I will install now and load the library.

```{r new library}
library(tidyverse)
```

And let's the gather formula do what we want.
```{r gather}
starwars%>% gather(name, height, mass, hair_color, skin_color, eye_color, birth_year, sex, gender, homeworld, species, fims, vehicles, convert = TRUE)
```

