---
title: "Data Practical Week 8"
author: "Bastien Nespolo"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Welcome in this report !
Here we load libraries to read our next folders.
```{r  message=FALSE, warning=FALSE}
library(readr)
library(dslabs)
library(dplyr)
library(knitr)
library(ggplot2)
library(tibble)
library(cluster)
library(patchwork)
```

## Dataset and variables'check

In this report we will start by loading our dataset. I chose to take my exclusive dataset that I create with my classmate Catia about paper plane task (presented in reports of week 6). I think this dataset is really good and fun for this exercise.
Let's load it.

```{r plane dataset}
plane<-read.table(file="plane.csv", header=TRUE, sep=";",dec=",") 
str(plane)
```

There are the same data from week 6. The dataset comes from A.Bangerter's class on coordination. We create this dataset to measure if an interactive-learning (teacher to student; condition 2) produces better performances rather than a non interactive-learning (Youtube to student; condition 1).These different learning conditions were our Explanatory variables. Performances was measured by recording paper planes' performances on 3 throws of a each paper plane created during the learning condition. The flying time and distance traveled by each plane were our measures and represent our Response variables.

## Correlations

Now we can see if there is a correlation between Explanatory and Responses variables.

First I will create an exclusive value : "Performances" that I create by multiplying the average distance with the average flying time. 
That's the performances for each participant.
```{r create performance value}
performance<-plane$average_distance*plane$average_flying_time
str(performance)
```

Now I will use this performances value to see if there is a correlation between performances and learning time. I think that the learning time is the best value to represent the different learning conditions. In that way, I will correlate my performances (response variable) with a value of different learning condition (explanatory variable). 
But first I just need to create the average of learning time for each roles (student which is learning condition 2 and teacher which is learning condition 1).

```{r student learning time average}
student_learning_average<-plane%>% filter(roles=="Student")
mean(student_learning_average$learning_time)
```
```{r teacher learning time average}
teacher_learning_average<-plane %>% filter(roles=="Teacher")
mean(teacher_learning_average$learning_time)
```
The average of student learning time is 6.833 and the one for teachers is 6.914... we will see if we use it.

Now we will know teacher's performances.
```{r performances of teachers}
performance_T<-teacher_learning_average$average_distance*teacher_learning_average$average_flying_time
```

And now we will know those for students.
```{r performances of students}
performance_S<-student_learning_average$average_distance*student_learning_average$average_flying_time
```

Now I can correlate my performances (response variable) with learning time (explanatory variable).
Let's do the correlation test
```{r correlation test for student}
cor.test(performance_S, student_learning_average$learning_time, use = "complete.obs")
```
...and now the same for teacher...
```{r correlation test for teacher}
cor.test(performance_T, teacher_learning_average$learning_time, use = "complete.obs")
```

### Results discussion

The correlation between performances of students and their learning time has a 
p-value = 0.35 which is not significant.
The correlation between performances of teachers and their learning time has 
p-value = 0.8858 which is not significant.

With these results, we can conclude that performances is independent of learning time. There is no correlation between performances and learning time. There is no causation in these correlations (which are not significant and negatives). And even if correlations were significant, we cannot say that there is a causation in a correlation. That's two separated things.

## Linear Model

Now, we will fit our model in a General Linear Model with all performances and learning time.
```{r linear model}
predictor1<-lm(performance~plane$learning_time)
summary(predictor1)
```
We can see that learning time is not a good predictor of performances. 
(Results : plane$learning_time   -68.87      94.15  -0.732   0.4739)

Now we can see it in a plot.
```{r plot of the linear model}
ggplot(plane,aes(performance,learning_time,label=rownames(plane),color=roles)) +
    geom_point() + labs(y ="Learning time (in minutes)" , x = "Plane's performance (in cm sec)") + geom_text(hjust = -0.4)+geom_smooth(method = "lm", se = TRUE,color="chartreuse")
```

Now we can see the plot which shows to us the performance of each plane on x axes (more is on the right, better it flown) and the learning time of each participant on y axes (more is high, longer he/her learned).
I think this plot could have several problems. First the fact that the unit cms (centimeters second) doesn't really exist. Or a second problem could be the fact that learning time is not a predictor of performance and in this plot design, we could think that participant / plane number 8 has a good result because is high but in reality it was a bad performance for a long learning time.
I think the plot model doesn't describe better the data than the table in Linear Model part.


### Additional comments

Don't hesitate to ask me more about this paper plane project if you want. We have a poster to share in which you can scan a QR code and see our data and our encoded interviews.
Thanks to have read my reports !
I hope you had fun.

Have a good end of day !

Bastien
