---
title: "Data Practical Week 7"
author: "Bastien Nespolo"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Welcome in this report !
Here we load libraries to read our next folders.
```{r  message=FALSE, warning=FALSE}
library(readr)
library(dslabs)
library(dplyr)
library(knitr)
library(ggplot2)
library(tibble)
library(cluster)
library(patchwork)
```

## Dataset

Now that I load some libraries I select a dataset about animal I can describe the variables. First I will indicate the meaning of the variables with the help of this source. If you click [here](https://stat.ethz.ch/R-manual/R-devel/library/cluster/html/animals.html) you can check the website which gave me these information.
```{r load the dataset}
data(animals)
str(animals)
```
## Meanings of variables

1. war =	warm-blooded
2. fly =	can fly
3. ver	= vertebrate
4. end =	endangered
5. gro	= live in groups
6. hai	= have hair

Variables are encoded as 1 = no, 2 = yes

Here is a list of these 20 animals observed. This list has been found [here](http://www.ru.ac.bd/stat/wp-content/uploads/sites/25/2019/03/503_09_Kaufman_Finding-Groups-in-Data-An-Introduction-to-Cluster-Analysis.pdf).
The list :  ant, bee, cat, caterpillar, chimpanzee, cow, duck, eagle, elephant, fly, frog, herring, lion, lizard, lobster, man, rabbit, salmon, spider, and whale.

## Describing variables

All my variables are "integer". Even if they are coded by numerical and entire numbers, they represent if yes or no they have the attribute of animal which correspond to a qualitative variable.

## Visualize the data

Now I will create several plots to see at which frequency an attribute is present in all animals. For that, I will use Barplots. Don't forget that 1 means no and 2 means yes. So for the second graph we can see that 16 animals don't fly and 4 animals fly.
```{r barplot frequency of attributes}
a<-ggplot(animals,aes(war)) + geom_bar() + scale_y_continuous(limits = c(0, 20))
b<-ggplot(animals,aes(fly)) + geom_bar() + scale_y_continuous(limits = c(0, 20))
c<-ggplot(animals,aes(ver)) + geom_bar() + scale_y_continuous(limits = c(0, 20))
d<-ggplot(animals,aes(end)) + geom_bar() + scale_y_continuous(limits = c(0, 20))
e<-ggplot(animals,aes(gro)) + geom_bar() + scale_y_continuous(limits = c(0, 20))
f<-ggplot(animals,aes(hai)) + geom_bar() + scale_y_continuous(limits = c(0, 20))

a+b+c+d+e+f
```

## Hypothesis

I'm wonder if warm-blooded animals are less endanger than those that are not ?
H0 will be that there is no correlation between warm-blood and endangered.

Or maybe those who lived in groups are less endangered than those who don't ?
H0 will be that living in group is not correlated with being endangered.

## Statisticals tests and analysis

We will use a correlation test between (1) warm-blooded and endangered animals and (2) between groups animal living in groups and endangered animals. The correlation test will tell us if having a warm-blood influences the survival of the species and in a second time if the fact that a species lives in group influences the fact that the species is endangered.
Let's do these correlations tests.
```{r correlation test (1)}
cor.test(animals$war, animals$end, use = "complete.obs")
```
The results for this first correlation test is significant. The p-value = 0.04829 so less than 0,05 which means that having warm-blooded seems to correlate with the  endangerment of the species.
Therefore, H0 is rejected.

Let's do the same for the second correlation test.
```{r correlation test (2)}
cor.test(animals$gro, animals$end, use = "complete.obs")
```
For these second results, we can see that the correlation test tells us that p-value = 0.4748. In that way, it means that living in group is not correlated with the endangerment of the species.
Therefore H0 can not be rejected.

Thanks and be happy to being part of a warm-blooded species !





